Simple repression draft

### 2020-05-30 doc/appendix_03_bayesian_inference.tex
transferred paragraphs from main text to SI

>>>>

\mmnote{These next 2 paragraphs should be SI, I think. Leaving here for
now to avoid a merge conflict w/ MRM.}

We found that fitting a single operator/aTc concentration at a
time with a single binding and unbinding rate did not yield a
stable inference for most of the possible operator/aTc
combinations. In other words, a single dataset could not
independently resolve the binding and unbinding rates, only their
ratio as set by the mean fold-change in
Figure~\ref{fig1:means_cartoons}. Only by making the assumption
of a single unique binding rate for each repressor copy number
and a single unique unbinding rate for each binding site, as done
in Figure~\ref{fig4:repressed_post_full}A, was it possible to
independently resolve the rates and not merely their ratios.

We also note that we found it necessary to exclude the very
weakly and very strongly repressed datasets from Jones et.\
al.~\cite{Jones2014}. In both cases there was, in a sense, not
enough information in the distriubtions for our inference
algorithm to extract, and their inclusion simply caused problems
for the MCMC sampler without yielding any new insight. For the
strongly repressed data (Oid, 10~ng/mL aTc), with $>$ 95\% of cells
with zero mRNA, there was quite literally very little data from
which to infer rates. And the weakly repressed data, all with the
repressor binding site O3, had an unbinding rate so fast that the
sampler essentially sampled from the prior; the likelihood had
negligible influence, meaning the data was not informing the
sampler in any meaninful way, so no inference was possible.
